---
title: "Forecast Trading Volumes - Crypto"
author: "Sulalitha Bowala"
date: "2023-08-02"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
rm(list=ls(all=TRUE)) # Remove objects from environment
```


```{r}
library(quantmod)
library(PerformanceAnalytics)
library(tidyverse)
```


## Download data

```{r}
getSymbols("BTC-USD", from = '2021-10-01',
           to = "2022-12-31",warnings = FALSE,
           auto.assign = TRUE)

getSymbols("ETH-USD", from = '2021-10-01',
           to = "2022-12-31",warnings = FALSE,
           auto.assign = TRUE)

getSymbols("USDT-USD", from = '2021-10-01',
           to = "2022-12-31",warnings = FALSE,
           auto.assign = TRUE)

getSymbols("BNB-USD", from = '2021-10-01',
           to = "2022-12-31",warnings = FALSE,
           auto.assign = TRUE)

head(`BTC-USD`)
```


```{r}
BTC = as.matrix.data.frame(`BTC-USD`)
head(BTC)
ETH = as.matrix.data.frame(`ETH-USD`)
USDT = as.matrix.data.frame(`USDT-USD`)
BNB = as.matrix.data.frame(`BNB-USD`)
```



## Calculate log return and log volume

```{r}
logReturn.BTC <- as.matrix(BTC[,6] %>% log %>% diff)
logReturn.ETH <- as.matrix(ETH[,6] %>% log %>% diff)
logReturn.USDT <- as.matrix(USDT[,6] %>% log %>% diff)
logReturn.BNB <- as.matrix(BNB[,6] %>% log %>% diff)

logVolume.BTC <- log(BTC[,5])
logVolume.ETH <- log(ETH[,5])
logVolume.USDT <- log(USDT[,5])
logVolume.BNB <- log(BNB[,5])

```


## data-driven volatility forecast

```{r}
# calculate sign correlation rho
rho.cal<-function(X){
  rho.hat<-cor(sign(X-mean(X)), X-mean(X))
  return(rho.hat)
}

ddvol <- function(data){ 
  ptm<-proc.time()
  alpha<-seq(0.01, 0.3, 0.01)
  t <- length(data)
  cut.t <- 50 ### how many l values
  X.cdf <- ecdf(data)
  rho<- rho.cal(data)
  mu <- mean(data)
  vol<- abs(data - mu)/(2*rho*sqrt(X.cdf(mu)*(1-X.cdf(mu))))
  MSE_alpha <- rep(0, length(alpha))
  sn <- rep(0, length(alpha))
  for(a in 1:length(alpha)){
    s <- mean(vol[1:cut.t])
    error<-rep(0, t)
    for(i in 1:t){
      error[i]<-vol[i]-s
      s<-alpha[a]*vol[i]+(1-alpha[a])*s
    }
    MSE_alpha[a]<-mean(error[-(1:cut.t)]^2)
    sn[a] <- s
  }
  dd.vol.fore <- sn[which.min(MSE_alpha)]
  rmse <- sqrt(min(MSE_alpha))
  return(c(dd.vol.fore, rmse, proc.time()-ptm))
}
```


```{r}
N <- nrow(logReturn.BTC)
step <- 90

ddvol.BTC<-c()
ddvol.ETH<-c()
ddvol.USDT<-c()
ddvol.BNB<-c()

for(i in 1:(N-90)){
  ddvol.BTC[[i]]<-ddvol(as.numeric(logReturn.BTC[i:(i+90)]))
}
ddvol.BTC.m <- as.data.frame(matrix(unlist(ddvol.BTC), nrow=length(ddvol.BTC), byrow=TRUE))[, 1:3]
colnames (ddvol.BTC.m) <- c("DDVF", "ERROR", "TIME")


for(i in 1:(N-90)){
  ddvol.ETH[[i]]<-ddvol(as.numeric(logReturn.ETH[i:(i+90)]))
}
ddvol.ETH.m <- as.data.frame(matrix(unlist(ddvol.ETH), nrow=length(ddvol.ETH), byrow=TRUE))[, 1:3]
colnames (ddvol.ETH.m) <- c("DDVF", "ERROR", "TIME")


for(i in 1:(N-90)){
  ddvol.USDT[[i]]<-ddvol(as.numeric(logReturn.USDT[i:(i+90)]))
}
ddvol.USDT.m <- as.data.frame(matrix(unlist(ddvol.USDT), nrow=length(ddvol.USDT), byrow=TRUE))[, 1:3]
colnames (ddvol.USDT.m) <- c("DDVF", "ERROR", "TIME")


for(i in 1:(N-90)){
  ddvol.BNB[[i]]<-ddvol(as.numeric(logReturn.BNB[i:(i+90)]))
}
ddvol.BNB.m <- as.data.frame(matrix(unlist(ddvol.BNB), nrow=length(ddvol.BNB), byrow=TRUE))[, 1:3]
colnames (ddvol.BNB.m) <- c("DDVF", "ERROR", "TIME")



logVolatility.BTC <- log(ddvol.BTC.m$DDVF[-1])
logVolatility.ETH <- log(ddvol.ETH.m$DDVF[-1])
logVolatility.USDT <- log(ddvol.USDT.m$DDVF[-1])
logVolatility.BNB <- log(ddvol.BNB.m$DDVF[-1])
```


## Constructing data frames with log volume, log return, and log volatiltity

## For BTC

```{r}
BTC.data <- cbind(logReturn.BTC[-c(1:91)], logVolume.BTC[-c(1:91)], logVolatility.BTC)
colnames(BTC.data) <- c("logReturn.BTC", "logVolume.BTC","logVolatility.BTC")
head(BTC.data)
tail(BTC.data)

acf(BTC.data[, 2])

pacf(BTC.data[, 2])

```


## For ETH

```{r}
ETH.data <- cbind(logReturn.ETH[-c(1:91)], logVolume.ETH[-c(1:91)], logVolatility.ETH)
colnames(ETH.data) <- c("logReturn.ETH", "logVolume.ETH","logVolatility.ETH")
head(ETH.data)
tail(ETH.data)

acf(ETH.data[, 2])

pacf(ETH.data[, 2])

```


## For USDT

```{r}
USDT.data <- cbind(logReturn.USDT[-c(1:91)], logVolume.USDT[-c(1:91)], logVolatility.USDT)
colnames(USDT.data) <- c("logReturn.USDT", "logVolume.USDT","logVolatility.USDT")
head(USDT.data)
tail(USDT.data)

acf(USDT.data[, 2])

pacf(USDT.data[, 2])

```




## For BNB

```{r}
BNB.data <- cbind(logReturn.BNB[-c(1:91)], logVolume.BNB[-c(1:91)], logVolatility.BNB)
colnames(BNB.data) <- c("logReturn.BNB", "logVolume.BNB","logVolatility.BNB")
head(BNB.data)
tail(BNB.data)

acf(BNB.data[, 2])

pacf(BNB.data[, 2])

```



## Indetifying train and test data

```{r}
ntest = round(nrow(BTC.data)*0.75)
ntest

train <- rep(NA, times = nrow(BTC.data))
BTC.data.Complete <- cbind(BTC.data, train)

for(i in 1:ntest){
  BTC.data.Complete[i,4]= "TRUE"
}
for(i in (ntest+1):(nrow(BTC.data))){
  BTC.data.Complete[i,4]= "FALSE"
}
#head(BTC.data.Complete)
#tail(BTC.data.Complete)


train <- rep(NA, times = nrow(ETH.data))
ETH.data.Complete <- cbind(ETH.data, train)

for(i in 1:ntest){
  ETH.data.Complete[i,4]= "TRUE"
}
for(i in (ntest+1):(nrow(BTC.data))){
  ETH.data.Complete[i,4]= "FALSE"
}


train <- rep(NA, times = nrow(USDT.data))
USDT.data.Complete <- cbind(USDT.data, train)

for(i in 1:ntest){
  USDT.data.Complete[i,4]= "TRUE"
}
for(i in (ntest+1):(nrow(BTC.data))){
  USDT.data.Complete[i,4]= "FALSE"
}


train <- rep(NA, times = nrow(BNB.data))
BNB.data.Complete <- cbind(BNB.data, train)

for(i in 1:ntest){
  BNB.data.Complete[i,4]= "TRUE"
}
for(i in (ntest+1):(nrow(BTC.data))){
  BNB.data.Complete[i,4]= "FALSE"
}

```


## Setup NN from the book

```{r}
istrain.BTC <- BTC.data.Complete[, "train"]
istrain.ETH <- ETH.data.Complete[, "train"]
istrain.USDT <- USDT.data.Complete[, "train"]
istrain.BNB <- BNB.data.Complete[, "train"]

xdata.BTC <- scale(BTC.data)
xdata.ETH <- scale(ETH.data)
xdata.USDT <- scale(USDT.data)
xdata.BNB <- scale(BNB.data)

```



```{r}
# Function to create lag values
lagm <- function(x, k = 1) {
n <- nrow(x)
pad <- matrix(NA , k, ncol(x))
rbind(pad , x[1:(n - k), ])
}
```



```{r}
## 11 peaks in ACF plot for BTC. Thus, we consider lag 19 for BTC.
arframe.BTC <- data.frame(log_volume.BTC = xdata.BTC[, "logVolume.BTC"],
L1.BTC = lagm(xdata.BTC , 1), L2.BTC = lagm(xdata.BTC , 2),
L3.BTC = lagm(xdata.BTC , 3), L4.BTC = lagm(xdata.BTC , 4),
L5.BTC = lagm(xdata.BTC , 5), L6.BTC = lagm(xdata.BTC , 6),
L7.BTC = lagm(xdata.BTC , 7), L8.BTC = lagm(xdata.BTC , 8),
L9.BTC = lagm(xdata.BTC , 9))


## 14 peaks in ACF plot for ETH. Thus, we consider lag 22 for ETH.
arframe.ETH <- data.frame(log_volume.ETH = xdata.ETH[, "logVolume.ETH"],
L1.ETH = lagm(xdata.ETH , 1), L2.ETH = lagm(xdata.ETH , 2),
L3.ETH = lagm(xdata.ETH , 3), L4.ETH = lagm(xdata.ETH , 4),
L5.ETH = lagm(xdata.ETH , 5), L6.ETH = lagm(xdata.ETH , 6),
L7.ETH = lagm(xdata.ETH , 7), L8.ETH = lagm(xdata.ETH , 8),
L9.ETH = lagm(xdata.ETH , 9), L10.ETH = lagm(xdata.ETH , 10),
L11.ETH = lagm(xdata.ETH , 11), L12.ETH = lagm(xdata.ETH , 12),
L13.ETH = lagm(xdata.ETH , 13), L14.ETH = lagm(xdata.ETH , 14), 
L15.ETH = lagm(xdata.ETH , 15), L16.ETH = lagm(xdata.ETH , 16), 
L17.ETH = lagm(xdata.ETH , 17), L18.ETH = lagm(xdata.ETH , 18), 
L19.ETH = lagm(xdata.ETH , 19), L20.ETH = lagm(xdata.ETH , 20), 
L21.ETH = lagm(xdata.ETH , 21), L22.ETH = lagm(xdata.ETH , 22))


## 4 peaks in ACF plot for USDT. Thus, we consider lag 22 for USDT.
arframe.USDT<- data.frame(log_volume.USDT = xdata.USDT[, "logVolume.USDT"],
L1.USDT = lagm(xdata.USDT , 1), L2.USDT = lagm(xdata.USDT , 2),
L3.USDT = lagm(xdata.USDT , 3), L4.USDT = lagm(xdata.USDT , 4),
L5.USDT = lagm(xdata.USDT , 5), L6.USDT = lagm(xdata.USDT , 6),
L7.USDT = lagm(xdata.USDT , 7), L8.USDT = lagm(xdata.USDT , 8),
L9.USDT = lagm(xdata.USDT , 9), L10.USDT = lagm(xdata.USDT , 10),
L11.USDT = lagm(xdata.USDT , 11), L12.USDT = lagm(xdata.USDT , 12),
L13.USDT = lagm(xdata.USDT , 13), L14.USDT = lagm(xdata.USDT , 14),
L15.USDT = lagm(xdata.USDT , 15), L16.USDT = lagm(xdata.USDT , 16),
L17.USDT = lagm(xdata.USDT , 17), L18.USDT = lagm(xdata.USDT , 18),
L19.USDT = lagm(xdata.USDT , 19), L20.USDT = lagm(xdata.USDT , 20),
L21.USDT = lagm(xdata.USDT , 21), L22.USDT = lagm(xdata.USDT , 22))


## 4 peaks in ACF plot for BNB. Thus, we consider lag 25 for BNB.
arframe.BNB<- data.frame(log_volume.BNB = xdata.BNB[, "logVolume.BNB"],
L1.BNB = lagm(xdata.BNB , 1), L2.BNB = lagm(xdata.BNB , 2),
L3.BNB = lagm(xdata.BNB , 3), L4.BNB = lagm(xdata.BNB , 4),
L5.BNB = lagm(xdata.BNB , 5), L6.BNB = lagm(xdata.BNB , 6),
L7.BNB = lagm(xdata.BNB , 7), L8.BNB = lagm(xdata.BNB , 8),
L9.BNB = lagm(xdata.BNB , 9), L10.BNB = lagm(xdata.BNB , 10),
L11.BNB = lagm(xdata.BNB , 11), L12.BNB = lagm(xdata.BNB , 12),
L13.BNB = lagm(xdata.BNB , 13), L14.BNB = lagm(xdata.BNB , 14),
L15.BNB = lagm(xdata.BNB , 15), L16.BNB = lagm(xdata.BNB , 16),
L17.BNB = lagm(xdata.BNB , 17), L18.BNB = lagm(xdata.BNB , 18),
L19.BNB = lagm(xdata.BNB , 19), L20.BNB = lagm(xdata.BNB , 20),
L21.BNB = lagm(xdata.BNB , 21), L22.BNB = lagm(xdata.BNB , 22),
L23.BNB = lagm(xdata.BNB , 23), L24.BNB = lagm(xdata.BNB , 24),
L25.BNB = lagm(xdata.BNB , 25))
```


```{r}
## remove empty rows and adjust istrain(s) accordingly.

arframe.BTC <- arframe.BTC[-(1:9), ]
istrain.BTC <- istrain.BTC[-(1:9)]

arframe.ETH <- arframe.ETH[-(1:22), ]
istrain.ETH <- istrain.ETH[-(1:22)]

arframe.USDT <- arframe.USDT[-(1:22), ]
istrain.USDT <- istrain.USDT[-(1:22)]

arframe.BNB <- arframe.BNB[-(1:25), ]
istrain.BNB <- istrain.BNB[-(1:25)]

```



```{r}
## To fit the RNN, we need to reshape these data

nBTC <- nrow(arframe.BTC)
xrnn.BTC <- data.matrix(arframe.BTC[, -1])
xrnn.BTC <- array(xrnn.BTC, c(nBTC, 3, 9))
xrnn.BTC <- xrnn.BTC[,, 9:1]
xrnn.BTC <- aperm(xrnn.BTC , c(1, 3, 2))
dim(xrnn.BTC)


nETH <- nrow(arframe.ETH)
xrnn.ETH <- data.matrix(arframe.ETH[, -1])
xrnn.ETH <- array(xrnn.ETH, c(nETH, 3, 22))
xrnn.ETH <- xrnn.ETH[,, 22:1]
xrnn.ETH <- aperm(xrnn.ETH , c(1, 3, 2))
dim(xrnn.ETH)


nUSDT <- nrow(arframe.USDT)
xrnn.USDT <- data.matrix(arframe.USDT[, -1])
xrnn.USDT <- array(xrnn.USDT, c(nUSDT, 3, 22))
xrnn.USDT <- xrnn.USDT[,, 22:1]
xrnn.USDT <- aperm(xrnn.USDT , c(1, 3, 2))
dim(xrnn.USDT)


nUSDT <- nrow(arframe.BNB)
xrnn.BNB <- data.matrix(arframe.BNB[, -1])
xrnn.BNB <- array(xrnn.BNB, c(nUSDT, 3, 25))
xrnn.BNB <- xrnn.BNB[,, 25:1]
xrnn.BNB <- aperm(xrnn.BNB , c(1, 3, 2))
dim(xrnn.BNB)
```


```{r, eval = FALSE}
myarray <- array( 1:24, dim=c(2,3,4),
 dimnames=list(One=c('a','b'), Two=c('A','B','C'), Three=1:4) )
myarray
aperm(myarray, c(3,1,2))
```


```{r}
library(reticulate)
#use_python('C:/Users/sulal/AppData/Local/Programs/Python/Python38')
use_python('C:/Users/sulal/AppData/Local/Programs/Python/Python38/Python.exe')

library(keras)
```



```{r}
#Now we are ready to proceed with the RNN, which uses 12 hidden units.

model.BTC <- keras_model_sequential () %>% layer_simple_rnn(units = 12, input_shape = list(9, 3),
dropout = 0.1, recurrent_dropout = 0.1) %>% layer_dense(units = 1)
model.BTC %>% compile(optimizer = optimizer_rmsprop (), loss = "mse")


model.ETH <- keras_model_sequential () %>% layer_simple_rnn(units = 12, input_shape = list(22, 3),
dropout = 0.1, recurrent_dropout = 0.1) %>% layer_dense(units = 1)
model.ETH %>% compile(optimizer = optimizer_rmsprop (), loss = "mse")


model.USDT <- keras_model_sequential () %>% layer_simple_rnn(units = 12, input_shape = list(22, 3),
dropout = 0.1, recurrent_dropout = 0.1) %>% layer_dense(units = 1)
model.USDT %>% compile(optimizer = optimizer_rmsprop (), loss = "mse")


model.BNB <- keras_model_sequential () %>% layer_simple_rnn(units = 12, input_shape = list(25, 3),
dropout = 0.1, recurrent_dropout = 0.1) %>% layer_dense(units = 1)
model.BNB %>% compile(optimizer = optimizer_rmsprop (), loss = "mse")
```


## Fit the model and forecast


## For BTC

```{r}

history.BTC <- model.BTC %>% fit(xrnn.BTC[(1:ntest) ,, ], arframe.BTC[(1:ntest) , "log_volume.BTC"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.BTC[((ntest+1):(dim(xrnn.BTC)[1])) ,, ], arframe.BTC[((ntest+1):(dim(xrnn.BTC)[1])) , "log_volume.BTC"]))

kpred.BTC <- predict(model.BTC, xrnn.BTC[((ntest+1):(dim(xrnn.BTC)[1])) ,, ])

## mean square error
MSE.BTC <- mean((kpred.BTC - arframe.BTC[((ntest+1):(dim(xrnn.BTC)[1])) , "log_volume.BTC"])^2)
MSE.BTC

## mean absolute deviation
MAD.BTC <- mean(abs(kpred.BTC - arframe.BTC[((ntest+1):(dim(xrnn.BTC)[1])) , "log_volume.BTC"]))
MAD.BTC
```



```{r}
plot(arframe.BTC[((ntest+1):(dim(xrnn.BTC)[1])) , "log_volume.BTC"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.BTC, col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```




## For ETH

```{r}

history.ETH <- model.ETH %>% fit(xrnn.ETH[(1:ntest) ,, ], arframe.ETH[(1:ntest) , "log_volume.ETH"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.ETH[((ntest+1):(dim(xrnn.ETH)[1])) ,, ], arframe.ETH[((ntest+1):(dim(xrnn.ETH)[1])) , "log_volume.ETH"]))

kpred.ETH <- predict(model.ETH, xrnn.ETH[((ntest+1):(dim(xrnn.ETH)[1])) ,, ])

## mean square error
MSE.ETH <- mean((kpred.ETH - arframe.ETH[((ntest+1):(dim(xrnn.ETH)[1])) , "log_volume.ETH"])^2)
MSE.ETH

## mean absolute deviation
MAD.ETH <- mean(abs(kpred.ETH - arframe.ETH[((ntest+1):(dim(xrnn.ETH)[1])) , "log_volume.ETH"]))
MAD.ETH
```



```{r}
plot(arframe.ETH[((ntest+1):(dim(xrnn.ETH)[1])) , "log_volume.ETH"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.ETH, col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```





## For USDT

```{r}

history.USDT <- model.USDT %>% fit(xrnn.USDT[(1:ntest) ,, ], arframe.USDT[(1:ntest) , "log_volume.USDT"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.USDT[((ntest+1):(dim(xrnn.USDT)[1])) ,, ], arframe.USDT[((ntest+1):(dim(xrnn.USDT)[1])) , "log_volume.USDT"]))

kpred.USDT <- predict(model.USDT, xrnn.USDT[((ntest+1):(dim(xrnn.USDT)[1])) ,, ])

## mean square error
MSE.USDT <- mean((kpred.USDT - arframe.USDT[((ntest+1):(dim(xrnn.USDT)[1])) , "log_volume.USDT"])^2)
MSE.USDT

## mean absolute deviation
MAD.USDT <- mean(abs(kpred.USDT - arframe.USDT[((ntest+1):(dim(xrnn.USDT)[1])) , "log_volume.USDT"]))
MAD.USDT
```



```{r}
plot(arframe.USDT[((ntest+1):(dim(xrnn.USDT)[1])) , "log_volume.USDT"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.USDT, col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```





## For BNB

```{r}

history.BNB <- model.BNB %>% fit(xrnn.BNB[(1:ntest) ,, ], arframe.BNB[(1:ntest) , "log_volume.BNB"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.BNB[((ntest+1):(dim(xrnn.BNB)[1])) ,, ], arframe.BNB[((ntest+1):(dim(xrnn.BNB)[1])) , "log_volume.BNB"]))

kpred.BNB <- predict(model.BNB, xrnn.BNB[((ntest+1):(dim(xrnn.BNB)[1])) ,, ])

## mean square error
MSE.BNB <- mean((kpred.BNB - arframe.BNB[((ntest+1):(dim(xrnn.BNB)[1])) , "log_volume.BNB"])^2)
MSE.BNB

## mean absolute deviation
MAD.BNB <- mean(abs(kpred.BNB - arframe.BNB[((ntest+1):(dim(xrnn.BNB)[1])) , "log_volume.BNB"]))
MAD.BNB
```



```{r}
plot(arframe.BNB[((ntest+1):(dim(xrnn.BNB)[1])) , "log_volume.BNB"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.BNB, col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```






## nnetar function from the forecast package

```{r}
library(forecast)
```



## for BTC

```{r}

trainID.BTC = which(BTC.data.Complete[,4]=="TRUE")
testID.BTC = which(BTC.data.Complete[,4]=="FALSE")

train.new.BTC = BTC.data.Complete[trainID.BTC,]
test.new.BTC = BTC.data.Complete[testID.BTC,]


fit.nn.BTC <- nnetar(as.numeric(train.new.BTC[,2]), xreg =  cbind(as.numeric(train.new.BTC[,1]), as.numeric(train.new.BTC[,3])), lambda="auto", decay = 0.1)

fit_test_cv.BTC <- CVar(as.numeric(train.new.BTC[,2]), xreg =  cbind(as.numeric(train.new.BTC[,1]), as.numeric(train.new.BTC[,3])), lambda="auto", decay = 0.1)

fit.nn.BTC

fore.nn.BTC <- forecast::forecast(fit.nn.BTC, xreg =  cbind(as.numeric(test.new.BTC[,1]), as.numeric(test.new.BTC[,3])), PI = TRUE)

## mean square error
MSE.nnetar.BTC <- mean((fore.nn.BTC$mean - as.numeric(test.new.BTC[,2]))^2)
MSE.nnetar.BTC

## mean absolute deviation
MAD.nnetar.BTC <- mean(abs(fore.nn.BTC$mean - as.numeric(test.new.BTC[,2])))
MAD.nnetar.BTC
```



```{r}
plot(as.numeric(test.new.BTC[,2]), col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(as.vector(fore.nn.BTC$mean), col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```





## for ETH

```{r}

trainID.ETH = which(ETH.data.Complete[,4]=="TRUE")
testID.ETH = which(ETH.data.Complete[,4]=="FALSE")

train.new.ETH = ETH.data.Complete[trainID.ETH,]
test.new.ETH = ETH.data.Complete[testID.ETH,]


fit.nn.ETH <- nnetar(as.numeric(train.new.ETH[,2]), xreg =  cbind(as.numeric(train.new.ETH[,1]), as.numeric(train.new.ETH[,3])), lambda="auto", decay = 0.1)

fit_test_cv.ETH <- CVar(as.numeric(train.new.ETH[,2]), xreg =  cbind(as.numeric(train.new.ETH[,1]), as.numeric(train.new.ETH[,3])), lambda="auto", decay = 0.1)

fit.nn.ETH

fore.nn.ETH <- forecast::forecast(fit.nn.ETH, xreg =  cbind(as.numeric(test.new.ETH[,1]), as.numeric(test.new.ETH[,3])), PI = TRUE)

## mean square error
MSE.nnetar.ETH <- mean((fore.nn.ETH$mean - as.numeric(test.new.ETH[,2]))^2)
MSE.nnetar.ETH

## mean absolute deviation
MAD.nnetar.ETH <- mean(abs(fore.nn.ETH$mean - as.numeric(test.new.ETH[,2])))
MAD.nnetar.ETH
```



```{r}
plot(as.numeric(test.new.ETH[,2]), col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(as.vector(fore.nn.ETH$mean), col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```








## for USDT

```{r}

trainID.USDT = which(USDT.data.Complete[,4]=="TRUE")
testID.USDT = which(USDT.data.Complete[,4]=="FALSE")

train.new.USDT = USDT.data.Complete[trainID.USDT,]
test.new.USDT = USDT.data.Complete[testID.USDT,]


fit.nn.USDT <- nnetar(as.numeric(train.new.USDT[,2]), xreg =  cbind(as.numeric(train.new.USDT[,1]), as.numeric(train.new.USDT[,3])), lambda="auto", decay = 0.1)

fit_test_cv.USDT <- CVar(as.numeric(train.new.USDT[,2]), xreg =  cbind(as.numeric(train.new.USDT[,1]), as.numeric(train.new.USDT[,3])), lambda="auto", decay = 0.1)

fit.nn.USDT

fore.nn.USDT <- forecast::forecast(fit.nn.USDT, xreg =  cbind(as.numeric(test.new.USDT[,1]), as.numeric(test.new.USDT[,3])), PI = TRUE)

## mean square error
MSE.nnetar.USDT <- mean((fore.nn.USDT$mean - as.numeric(test.new.USDT[,2]))^2)
MSE.nnetar.USDT

## mean absolute deviation
MAD.nnetar.USDT <- mean(abs(fore.nn.USDT$mean - as.numeric(test.new.USDT[,2])))
MAD.nnetar.USDT
```



```{r}
plot(as.numeric(test.new.USDT[,2]), col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(as.vector(fore.nn.USDT$mean), col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```





## for BNB

```{r}

trainID.BNB = which(BNB.data.Complete[,4]=="TRUE")
testID.BNB = which(BNB.data.Complete[,4]=="FALSE")

train.new.BNB = BNB.data.Complete[trainID.BNB,]
test.new.BNB = BNB.data.Complete[testID.BNB,]


fit.nn.BNB <- nnetar(as.numeric(train.new.BNB[,2]), xreg =  cbind(as.numeric(train.new.BNB[,1]), as.numeric(train.new.BNB[,3])), lambda="auto", decay = 0.1)

fit_test_cv.BNB <- CVar(as.numeric(train.new.BNB[,2]), xreg =  cbind(as.numeric(train.new.BNB[,1]), as.numeric(train.new.BNB[,3])), lambda="auto", decay = 0.1)

fit.nn.BNB

fore.nn.BNB <- forecast::forecast(fit.nn.BNB, xreg =  cbind(as.numeric(test.new.BNB[,1]), as.numeric(test.new.BNB[,3])), PI = TRUE)

## mean square error
MSE.nnetar.BNB <- mean((fore.nn.BNB$mean - as.numeric(test.new.BNB[,2]))^2)
MSE.nnetar.BNB

## mean absolute deviation
MAD.nnetar.BNB <- mean(abs(fore.nn.BNB$mean - as.numeric(test.new.BNB[,2])))
MAD.nnetar.BNB
```



```{r}
plot(as.numeric(test.new.BNB[,2]), col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(as.vector(fore.nn.BNB$mean), col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```





## NN with two layers. each layer has 24 neurons


## BTC

```{r}
model.BTC.new <- keras_model_sequential() %>%
  layer_simple_rnn(units = 24, input_shape = list(9, 3),
                   dropout = 0.1, recurrent_dropout = 0.1,
                   return_sequences = TRUE) %>%
  layer_simple_rnn(units = 24,
                   dropout = 0.1, recurrent_dropout = 0.1) %>%
  layer_dense(units = 1)

model.BTC.new %>% compile(optimizer = optimizer_rmsprop(), loss = "mse")


history.BTC.new <- model.BTC.new %>% fit(xrnn.BTC[(1:ntest) ,, ], arframe.BTC[(1:ntest) , "log_volume.BTC"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.BTC[((ntest+1):(dim(xrnn.BTC)[1])) ,, ], arframe.BTC[((ntest+1):(dim(xrnn.BTC)[1])) , "log_volume.BTC"]))

kpred.BTC.new <- predict(model.BTC.new, xrnn.BTC[((ntest+1):(dim(xrnn.BTC)[1])) ,, ])

## mean square error
MSE.BTC.new <- mean((kpred.BTC.new - arframe.BTC[((ntest+1):(dim(xrnn.BTC)[1])) , "log_volume.BTC"])^2)
MSE.BTC.new

## mean absolute deviation
MAD.BTC.new <- mean(abs(kpred.BTC.new - arframe.BTC[((ntest+1):(dim(xrnn.BTC)[1])) , "log_volume.BTC"]))
MAD.BTC.new

```



```{r}
plot(arframe.BTC[((ntest+1):(dim(xrnn.BTC)[1])) , "log_volume.BTC"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.BTC.new, col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```




## ETH

```{r}
model.ETH.new <- keras_model_sequential() %>%
  layer_simple_rnn(units = 24, input_shape = list(22, 3),
                   dropout = 0.1, recurrent_dropout = 0.1,
                   return_sequences = TRUE) %>%
  layer_simple_rnn(units = 24,
                   dropout = 0.1, recurrent_dropout = 0.1) %>%
  layer_dense(units = 1)

model.ETH.new %>% compile(optimizer = optimizer_rmsprop(), loss = "mse")


history.ETH.new <- model.ETH.new %>% fit(xrnn.ETH[(1:ntest) ,, ], arframe.ETH[(1:ntest) , "log_volume.ETH"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.ETH[((ntest+1):(dim(xrnn.ETH)[1])) ,, ], arframe.ETH[((ntest+1):(dim(xrnn.ETH)[1])) , "log_volume.ETH"]))

kpred.ETH.new <- predict(model.ETH.new, xrnn.ETH[((ntest+1):(dim(xrnn.ETH)[1])) ,, ])

## mean square error
MSE.ETH.new <- mean((kpred.ETH.new - arframe.ETH[((ntest+1):(dim(xrnn.ETH)[1])) , "log_volume.ETH"])^2)
MSE.ETH.new

## mean absolute deviation
MAD.ETH.new <- mean(abs(kpred.ETH.new - arframe.ETH[((ntest+1):(dim(xrnn.ETH)[1])) , "log_volume.ETH"]))
MAD.ETH.new

```



```{r}
plot(arframe.ETH[((ntest+1):(dim(xrnn.ETH)[1])) , "log_volume.ETH"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.ETH.new, col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```





## USDT

```{r}
model.USDT.new <- keras_model_sequential() %>%
  layer_simple_rnn(units = 24, input_shape = list(22, 3),
                   dropout = 0.1, recurrent_dropout = 0.1,
                   return_sequences = TRUE) %>%
  layer_simple_rnn(units = 24,
                   dropout = 0.1, recurrent_dropout = 0.1) %>%
  layer_dense(units = 1)

model.USDT.new %>% compile(optimizer = optimizer_rmsprop(), loss = "mse")


history.USDT.new <- model.USDT.new %>% fit(xrnn.USDT[(1:ntest) ,, ], arframe.USDT[(1:ntest) , "log_volume.USDT"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.USDT[((ntest+1):(dim(xrnn.USDT)[1])) ,, ], arframe.USDT[((ntest+1):(dim(xrnn.USDT)[1])) , "log_volume.USDT"]))

kpred.USDT.new <- predict(model.USDT.new, xrnn.USDT[((ntest+1):(dim(xrnn.USDT)[1])) ,, ])

## mean square error
MSE.USDT.new <- mean((kpred.USDT.new - arframe.USDT[((ntest+1):(dim(xrnn.USDT)[1])) , "log_volume.USDT"])^2)
MSE.USDT.new

## mean absolute deviation
MAD.USDT.new <- mean(abs(kpred.USDT.new - arframe.USDT[((ntest+1):(dim(xrnn.USDT)[1])) , "log_volume.USDT"]))
MAD.USDT.new

```



```{r}
plot(arframe.USDT[((ntest+1):(dim(xrnn.USDT)[1])) , "log_volume.USDT"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.USDT.new, col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```






## BNB

```{r}
model.BNB.new <- keras_model_sequential() %>%
  layer_simple_rnn(units = 24, input_shape = list(25, 3),
                   dropout = 0.1, recurrent_dropout = 0.1,
                   return_sequences = TRUE) %>%
  layer_simple_rnn(units = 24,
                   dropout = 0.1, recurrent_dropout = 0.1) %>%
  layer_dense(units = 1)

model.BNB.new %>% compile(optimizer = optimizer_rmsprop(), loss = "mse")


history.BNB.new <- model.BNB.new %>% fit(xrnn.BNB[(1:ntest) ,, ], arframe.BNB[(1:ntest) , "log_volume.BNB"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.BNB[((ntest+1):(dim(xrnn.BNB)[1])) ,, ], arframe.BNB[((ntest+1):(dim(xrnn.BNB)[1])) , "log_volume.BNB"]))

kpred.BNB.new <- predict(model.BNB.new, xrnn.BNB[((ntest+1):(dim(xrnn.BNB)[1])) ,, ])

## mean square error
MSE.BNB.new <- mean((kpred.BNB.new - arframe.BNB[((ntest+1):(dim(xrnn.BNB)[1])) , "log_volume.BNB"])^2)
MSE.BNB.new

## mean absolute deviation
MAD.BNB.new <- mean(abs(kpred.BNB.new - arframe.BNB[((ntest+1):(dim(xrnn.BNB)[1])) , "log_volume.BNB"]))
MAD.BNB.new

```



```{r}
plot(arframe.BNB[((ntest+1):(dim(xrnn.BNB)[1])) , "log_volume.BNB"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.BNB.new, col="blue")
legend("topright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```

