---
title: "Forecast Trading Volumes - Stocks"
author: "Sulalitha Bowala"
date: "2023-08-02"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
rm(list=ls(all=TRUE)) # Remove objects from environment
```


```{r}
library(quantmod)
library(PerformanceAnalytics)
library(tidyverse)
```


## Download data

```{r}
getSymbols("AAPL", from = '2021-10-01',
           to = "2022-12-31",warnings = FALSE,
           auto.assign = TRUE)


getSymbols("MSFT", from = '2021-10-01',
           to = "2022-12-31",warnings = FALSE,
           auto.assign = TRUE)

getSymbols("NVDA", from = '2021-10-01',
           to = "2022-12-31",warnings = FALSE,
           auto.assign = TRUE)

getSymbols("INTC", from = '2021-10-01',
           to = "2022-12-31",warnings = FALSE,
           auto.assign = TRUE)
head(AAPL)
```


```{r}
AAPL = as.matrix.data.frame(AAPL)
head(AAPL)
MSFT = as.matrix.data.frame(MSFT)
NVDA = as.matrix.data.frame(NVDA)
INTC = as.matrix.data.frame(INTC)
```



## Calculate log return and log volume

```{r}
logReturn.AAPL <- as.matrix(AAPL[,6] %>% log %>% diff)
logReturn.MSFT <- as.matrix(MSFT[,6] %>% log %>% diff)
logReturn.NVDA <- as.matrix(NVDA[,6] %>% log %>% diff)
logReturn.INTC <- as.matrix(INTC[,6] %>% log %>% diff)

logVolume.AAPL <- log(AAPL[,5])
logVolume.MSFT <- log(MSFT[,5])
logVolume.NVDA <- log(NVDA[,5])
logVolume.INTC <- log(INTC[,5])

```


## data-driven volatility forecast

```{r}
# calculate sign correlation rho
rho.cal<-function(X){
  rho.hat<-cor(sign(X-mean(X)), X-mean(X))
  return(rho.hat)
}

ddvol <- function(data){ 
  ptm<-proc.time()
  alpha<-seq(0.01, 0.3, 0.01)
  t <- length(data)
  cut.t <- 50 ### how many l values
  X.cdf <- ecdf(data)
  rho<- rho.cal(data)
  mu <- mean(data)
  vol<- abs(data - mu)/(2*rho*sqrt(X.cdf(mu)*(1-X.cdf(mu))))
  MSE_alpha <- rep(0, length(alpha))
  sn <- rep(0, length(alpha))
  for(a in 1:length(alpha)){
    s <- mean(vol[1:cut.t])
    error<-rep(0, t)
    for(i in 1:t){
      error[i]<-vol[i]-s
      s<-alpha[a]*vol[i]+(1-alpha[a])*s
    }
    MSE_alpha[a]<-mean(error[-(1:cut.t)]^2)
    sn[a] <- s
  }
  dd.vol.fore <- sn[which.min(MSE_alpha)]
  rmse <- sqrt(min(MSE_alpha))
  return(c(dd.vol.fore, rmse, proc.time()-ptm))
}
```


```{r}
N <- nrow(logReturn.AAPL)
step <- 63

ddvol.AAPL<-c()
ddvol.MSFT<-c()
ddvol.NVDA<-c()
ddvol.INTC<-c()

for(i in 1:(N-63)){
  ddvol.AAPL[[i]]<-ddvol(as.numeric(logReturn.AAPL[i:(i+63)]))
}
ddvol.AAPL.m <- as.data.frame(matrix(unlist(ddvol.AAPL), nrow=length(ddvol.AAPL), byrow=TRUE))[, 1:3]
colnames (ddvol.AAPL.m) <- c("DDVF", "ERROR", "TIME")


for(i in 1:(N-63)){
  ddvol.MSFT[[i]]<-ddvol(as.numeric(logReturn.MSFT[i:(i+63)]))
}
ddvol.MSFT.m <- as.data.frame(matrix(unlist(ddvol.MSFT), nrow=length(ddvol.MSFT), byrow=TRUE))[, 1:3]
colnames (ddvol.MSFT.m) <- c("DDVF", "ERROR", "TIME")


for(i in 1:(N-63)){
  ddvol.NVDA[[i]]<-ddvol(as.numeric(logReturn.NVDA[i:(i+63)]))
}
ddvol.NVDA.m <- as.data.frame(matrix(unlist(ddvol.NVDA), nrow=length(ddvol.NVDA), byrow=TRUE))[, 1:3]
colnames (ddvol.NVDA.m) <- c("DDVF", "ERROR", "TIME")


for(i in 1:(N-63)){
  ddvol.INTC[[i]]<-ddvol(as.numeric(logReturn.INTC[i:(i+63)]))
}
ddvol.INTC.m <- as.data.frame(matrix(unlist(ddvol.INTC), nrow=length(ddvol.INTC), byrow=TRUE))[, 1:3]
colnames (ddvol.INTC.m) <- c("DDVF", "ERROR", "TIME")



logVolatility.AAPL <- log(ddvol.AAPL.m$DDVF[-1])
logVolatility.MSFT <- log(ddvol.MSFT.m$DDVF[-1])
logVolatility.NVDA <- log(ddvol.NVDA.m$DDVF[-1])
logVolatility.INTC <- log(ddvol.INTC.m$DDVF[-1])
```


## Constructing data frames with log volume, log return, and log volatiltity

## For AAPL

```{r}
AAPL.data <- cbind(logReturn.AAPL[-c(1:64)], logVolume.AAPL[-c(1:64)], logVolatility.AAPL)
colnames(AAPL.data) <- c("logReturn.AAPL", "logVolume.AAPL","logVolatility.AAPL")
head(AAPL.data)
tail(AAPL.data)

acf(AAPL.data[, 2])

pacf(AAPL.data[, 2])

```


## For MSFT

```{r}
MSFT.data <- cbind(logReturn.MSFT[-c(1:64)], logVolume.MSFT[-c(1:64)], logVolatility.MSFT)
colnames(MSFT.data) <- c("logReturn.MSFT", "logVolume.MSFT","logVolatility.MSFT")
head(MSFT.data)
tail(MSFT.data)

acf(MSFT.data[, 2])

pacf(MSFT.data[, 2])

```


## For NVDA

```{r}
NVDA.data <- cbind(logReturn.NVDA[-c(1:64)], logVolume.NVDA[-c(1:64)], logVolatility.NVDA)
colnames(NVDA.data) <- c("logReturn.NVDA", "logVolume.NVDA","logVolatility.NVDA")
head(NVDA.data)
tail(NVDA.data)

acf(NVDA.data[, 2])

pacf(NVDA.data[, 2])

```




## For INTC

```{r}
INTC.data <- cbind(logReturn.INTC[-c(1:64)], logVolume.INTC[-c(1:64)], logVolatility.INTC)
colnames(INTC.data) <- c("logReturn.INTC", "logVolume.INTC","logVolatility.INTC")
head(INTC.data)
tail(INTC.data)

acf(INTC.data[, 2])

pacf(INTC.data[, 2])

```



## Indetifying train and test data

```{r}
ntest = round(nrow(AAPL.data)*0.75)
ntest

train <- rep(NA, times = nrow(AAPL.data))
AAPL.data.Complete <- cbind(AAPL.data, train)

for(i in 1:ntest){
  AAPL.data.Complete[i,4]= "TRUE"
}
for(i in (ntest+1):(nrow(AAPL.data))){
  AAPL.data.Complete[i,4]= "FALSE"
}
#head(AAPL.data.Complete)
#tail(AAPL.data.Complete)


train <- rep(NA, times = nrow(MSFT.data))
MSFT.data.Complete <- cbind(MSFT.data, train)

for(i in 1:ntest){
  MSFT.data.Complete[i,4]= "TRUE"
}
for(i in (ntest+1):(nrow(AAPL.data))){
  MSFT.data.Complete[i,4]= "FALSE"
}


train <- rep(NA, times = nrow(NVDA.data))
NVDA.data.Complete <- cbind(NVDA.data, train)

for(i in 1:ntest){
  NVDA.data.Complete[i,4]= "TRUE"
}
for(i in (ntest+1):(nrow(AAPL.data))){
  NVDA.data.Complete[i,4]= "FALSE"
}


train <- rep(NA, times = nrow(INTC.data))
INTC.data.Complete <- cbind(INTC.data, train)

for(i in 1:ntest){
  INTC.data.Complete[i,4]= "TRUE"
}
for(i in (ntest+1):(nrow(AAPL.data))){
  INTC.data.Complete[i,4]= "FALSE"
}

```


## Setup NN from the book

```{r}
istrain.AAPL <- AAPL.data.Complete[, "train"]
istrain.MSFT <- MSFT.data.Complete[, "train"]
istrain.NVDA <- NVDA.data.Complete[, "train"]
istrain.INTC <- INTC.data.Complete[, "train"]

xdata.AAPL <- scale(AAPL.data)
xdata.MSFT <- scale(MSFT.data)
xdata.NVDA <- scale(NVDA.data)
xdata.INTC <- scale(INTC.data)

```



```{r}
# Function to create lag values
lagm <- function(x, k = 1) {
n <- nrow(x)
pad <- matrix(NA , k, ncol(x))
rbind(pad , x[1:(n - k), ])
}
```



```{r}
## 11 peaks in ACF plot for AAPL. Thus, we consider lag 11 for AAPL.
arframe.AAPL <- data.frame(log_volume.AAPL = xdata.AAPL[, "logVolume.AAPL"],
L1.AAPL = lagm(xdata.AAPL , 1), L2.AAPL = lagm(xdata.AAPL , 2),
L3.AAPL = lagm(xdata.AAPL , 3), L4.AAPL = lagm(xdata.AAPL , 4),
L5.AAPL = lagm(xdata.AAPL , 5), L6.AAPL = lagm(xdata.AAPL , 6),
L7.AAPL = lagm(xdata.AAPL , 7), L8.AAPL = lagm(xdata.AAPL , 8),
L9.AAPL = lagm(xdata.AAPL , 9), L10.AAPL = lagm(xdata.AAPL , 10),
L11.AAPL = lagm(xdata.AAPL , 11))


## 14 peaks in ACF plot for MSFT. Thus, we consider lag 14 for MSFT.
arframe.MSFT <- data.frame(log_volume.MSFT = xdata.MSFT[, "logVolume.MSFT"],
L1.MSFT = lagm(xdata.MSFT , 1), L2.MSFT = lagm(xdata.MSFT , 2),
L3.MSFT = lagm(xdata.MSFT , 3), L4.MSFT = lagm(xdata.MSFT , 4),
L5.MSFT = lagm(xdata.MSFT , 5), L6.MSFT = lagm(xdata.MSFT , 6),
L7.MSFT = lagm(xdata.MSFT , 7), L8.MSFT = lagm(xdata.MSFT , 8),
L9.MSFT = lagm(xdata.MSFT , 9), L10.MSFT = lagm(xdata.MSFT , 10),
L11.MSFT = lagm(xdata.MSFT , 11), L12.MSFT = lagm(xdata.MSFT , 12),
L13.MSFT = lagm(xdata.MSFT , 13), L14.MSFT = lagm(xdata.MSFT , 14))


## 4 peaks in ACF plot for NVDA. Thus, we consider lag 4 for NVDA.
arframe.NVDA<- data.frame(log_volume.NVDA = xdata.NVDA[, "logVolume.NVDA"],
L1.NVDA = lagm(xdata.NVDA , 1), L2.NVDA = lagm(xdata.NVDA , 2),
L3.NVDA = lagm(xdata.NVDA , 3), L4.NVDA = lagm(xdata.NVDA , 4))


## 4 peaks in ACF plot for INTC. Thus, we consider lag 4 for INTC.
arframe.INTC<- data.frame(log_volume.INTC = xdata.INTC[, "logVolume.INTC"],
L1.INTC = lagm(xdata.INTC , 1), L2.INTC = lagm(xdata.INTC , 2),
L3.INTC = lagm(xdata.INTC , 3), L4.INTC = lagm(xdata.INTC , 4))
```


```{r}
## remove empty rows and adjust istrain(s) accordingly.

arframe.AAPL <- arframe.AAPL[-(1:11), ]
istrain.AAPL <- istrain.AAPL[-(1:11)]

arframe.MSFT <- arframe.MSFT[-(1:14), ]
istrain.MSFT <- istrain.MSFT[-(1:14)]

arframe.NVDA <- arframe.NVDA[-(1:4), ]
istrain.NVDA <- istrain.NVDA[-(1:4)]

arframe.INTC <- arframe.INTC[-(1:4), ]
istrain.INTC <- istrain.INTC[-(1:4)]

```



```{r}
## To fit the RNN, we need to reshape these data

nAAPL <- nrow(arframe.AAPL)
xrnn.AAPL <- data.matrix(arframe.AAPL[, -1])
xrnn.AAPL <- array(xrnn.AAPL, c(nAAPL, 3, 11))
xrnn.AAPL <- xrnn.AAPL[,, 11:1]
xrnn.AAPL <- aperm(xrnn.AAPL , c(1, 3, 2))
dim(xrnn.AAPL)


nMSFT <- nrow(arframe.MSFT)
xrnn.MSFT <- data.matrix(arframe.MSFT[, -1])
xrnn.MSFT <- array(xrnn.MSFT, c(nMSFT, 3, 14))
xrnn.MSFT <- xrnn.MSFT[,, 14:1]
xrnn.MSFT <- aperm(xrnn.MSFT , c(1, 3, 2))
dim(xrnn.MSFT)


nNVDA <- nrow(arframe.NVDA)
xrnn.NVDA <- data.matrix(arframe.NVDA[, -1])
xrnn.NVDA <- array(xrnn.NVDA, c(nNVDA, 3, 4))
xrnn.NVDA <- xrnn.NVDA[,, 4:1]
xrnn.NVDA <- aperm(xrnn.NVDA , c(1, 3, 2))
dim(xrnn.NVDA)


nNVDA <- nrow(arframe.INTC)
xrnn.INTC <- data.matrix(arframe.INTC[, -1])
xrnn.INTC <- array(xrnn.INTC, c(nNVDA, 3, 4))
xrnn.INTC <- xrnn.INTC[,, 4:1]
xrnn.INTC <- aperm(xrnn.INTC , c(1, 3, 2))
dim(xrnn.INTC)
```


```{r, eval = FALSE}
myarray <- array( 1:24, dim=c(2,3,4),
 dimnames=list(One=c('a','b'), Two=c('A','B','C'), Three=1:4) )
myarray
aperm(myarray, c(3,1,2))
```


```{r}
library(reticulate)
#use_python('C:/Users/sulal/AppData/Local/Programs/Python/Python38')
use_python('C:/Users/sulal/AppData/Local/Programs/Python/Python38/Python.exe')

library(keras)
```



```{r}
#Now we are ready to proceed with the RNN, which uses 12 hidden units.

model.AAPL <- keras_model_sequential () %>% layer_simple_rnn(units = 12, input_shape = list(11, 3),
dropout = 0.1, recurrent_dropout = 0.1) %>% layer_dense(units = 1)
model.AAPL %>% compile(optimizer = optimizer_rmsprop (), loss = "mse")


model.MSFT <- keras_model_sequential () %>% layer_simple_rnn(units = 12, input_shape = list(14, 3),
dropout = 0.1, recurrent_dropout = 0.1) %>% layer_dense(units = 1)
model.MSFT %>% compile(optimizer = optimizer_rmsprop (), loss = "mse")


model.NVDA <- keras_model_sequential () %>% layer_simple_rnn(units = 12, input_shape = list(4, 3),
dropout = 0.1, recurrent_dropout = 0.1) %>% layer_dense(units = 1)
model.NVDA %>% compile(optimizer = optimizer_rmsprop (), loss = "mse")


model.INTC <- keras_model_sequential () %>% layer_simple_rnn(units = 12, input_shape = list(4, 3),
dropout = 0.1, recurrent_dropout = 0.1) %>% layer_dense(units = 1)
model.INTC %>% compile(optimizer = optimizer_rmsprop (), loss = "mse")
```


## Fit the model and forecast


## For AAPL

```{r}

history.AAPL <- model.AAPL %>% fit(xrnn.AAPL[(1:ntest) ,, ], arframe.AAPL[(1:ntest) , "log_volume.AAPL"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) ,, ], arframe.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) , "log_volume.AAPL"]))

kpred.AAPL <- predict(model.AAPL, xrnn.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) ,, ])

## mean square error
MSE.AAPL <- mean((kpred.AAPL - arframe.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) , "log_volume.AAPL"])^2)
MSE.AAPL

## mean absolute deviation
MAD.AAPL <- mean(abs(kpred.AAPL - arframe.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) , "log_volume.AAPL"]))
MAD.AAPL
```


```{r}
plot(arframe.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) , "log_volume.AAPL"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.AAPL, col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```



## For MSFT

```{r}

history.MSFT <- model.MSFT %>% fit(xrnn.MSFT[(1:ntest) ,, ], arframe.MSFT[(1:ntest) , "log_volume.MSFT"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) ,, ], arframe.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) , "log_volume.MSFT"]))

kpred.MSFT <- predict(model.MSFT, xrnn.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) ,, ])

## mean square error
MSE.MSFT <- mean((kpred.MSFT - arframe.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) , "log_volume.MSFT"])^2)
MSE.MSFT

## mean absolute deviation
MAD.MSFT <- mean(abs(kpred.MSFT - arframe.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) , "log_volume.MSFT"]))
MAD.MSFT
```


```{r}
plot(arframe.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) , "log_volume.MSFT"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.MSFT, col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```



## For NVDA

```{r}

history.NVDA <- model.NVDA %>% fit(xrnn.NVDA[(1:ntest) ,, ], arframe.NVDA[(1:ntest) , "log_volume.NVDA"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) ,, ], arframe.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) , "log_volume.NVDA"]))

kpred.NVDA <- predict(model.NVDA, xrnn.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) ,, ])

## mean square error
MSE.NVDA <- mean((kpred.NVDA - arframe.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) , "log_volume.NVDA"])^2)
MSE.NVDA

## mean absolute deviation
MAD.NVDA <- mean(abs(kpred.NVDA - arframe.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) , "log_volume.NVDA"]))
MAD.NVDA
```



```{r}
plot(arframe.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) , "log_volume.NVDA"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.NVDA, col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```



## For INTC

```{r}

history.INTC <- model.INTC %>% fit(xrnn.INTC[(1:ntest) ,, ], arframe.INTC[(1:ntest) , "log_volume.INTC"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.INTC[((ntest+1):(dim(xrnn.INTC)[1])) ,, ], arframe.INTC[((ntest+1):(dim(xrnn.INTC)[1])) , "log_volume.INTC"]))

kpred.INTC <- predict(model.INTC, xrnn.INTC[((ntest+1):(dim(xrnn.INTC)[1])) ,, ])

## mean square error
MSE.INTC <- mean((kpred.INTC - arframe.INTC[((ntest+1):(dim(xrnn.INTC)[1])) , "log_volume.INTC"])^2)
MSE.INTC

## mean absolute deviation
MAD.INTC <- mean(abs(kpred.INTC - arframe.INTC[((ntest+1):(dim(xrnn.INTC)[1])) , "log_volume.INTC"]))
MAD.INTC
```



```{r}
plot(arframe.INTC[((ntest+1):(dim(xrnn.INTC)[1])) , "log_volume.INTC"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.INTC, col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```



## nnetar function from the forecast package

```{r}
library(forecast)
```



## for AAPL

```{r}

trainID.AAPL = which(AAPL.data.Complete[,4]=="TRUE")
testID.AAPL = which(AAPL.data.Complete[,4]=="FALSE")

train.new.AAPL = AAPL.data.Complete[trainID.AAPL,]
test.new.AAPL = AAPL.data.Complete[testID.AAPL,]


fit.nn.AAPL <- nnetar(as.numeric(train.new.AAPL[,2]), xreg =  cbind(as.numeric(train.new.AAPL[,1]), as.numeric(train.new.AAPL[,3])), lambda="auto", decay = 0.1)

fit_test_cv.AAPL <- CVar(as.numeric(train.new.AAPL[,2]), xreg =  cbind(as.numeric(train.new.AAPL[,1]), as.numeric(train.new.AAPL[,3])), lambda="auto", decay = 0.1)

fit.nn.AAPL

fore.nn.AAPL <- forecast::forecast(fit.nn.AAPL, xreg =  cbind(as.numeric(test.new.AAPL[,1]), as.numeric(test.new.AAPL[,3])), PI = TRUE)

## mean square error
MSE.nnetar.AAPL <- mean((fore.nn.AAPL$mean - as.numeric(test.new.AAPL[,2]))^2)
MSE.nnetar.AAPL

## mean absolute deviation
MAD.nnetar.AAPL <- mean(abs(fore.nn.AAPL$mean - as.numeric(test.new.AAPL[,2])))
MAD.nnetar.AAPL
```



```{r}
plot(as.numeric(test.new.AAPL[,2]), col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(as.vector(fore.nn.AAPL$mean), col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```



## for MSFT

```{r}

trainID.MSFT = which(MSFT.data.Complete[,4]=="TRUE")
testID.MSFT = which(MSFT.data.Complete[,4]=="FALSE")

train.new.MSFT = MSFT.data.Complete[trainID.MSFT,]
test.new.MSFT = MSFT.data.Complete[testID.MSFT,]


fit.nn.MSFT <- nnetar(as.numeric(train.new.MSFT[,2]), xreg =  cbind(as.numeric(train.new.MSFT[,1]), as.numeric(train.new.MSFT[,3])), lambda="auto", decay = 0.1)

fit_test_cv.MSFT <- CVar(as.numeric(train.new.MSFT[,2]), xreg =  cbind(as.numeric(train.new.MSFT[,1]), as.numeric(train.new.MSFT[,3])), lambda="auto", decay = 0.1)

fit.nn.MSFT

fore.nn.MSFT <- forecast::forecast(fit.nn.MSFT, xreg =  cbind(as.numeric(test.new.MSFT[,1]), as.numeric(test.new.MSFT[,3])), PI = TRUE)

## mean square error
MSE.nnetar.MSFT <- mean((fore.nn.MSFT$mean - as.numeric(test.new.MSFT[,2]))^2)
MSE.nnetar.MSFT

## mean absolute deviation
MAD.nnetar.MSFT <- mean(abs(fore.nn.MSFT$mean - as.numeric(test.new.MSFT[,2])))
MAD.nnetar.MSFT
```



```{r}
plot(as.numeric(test.new.MSFT[,2]), col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(as.vector(fore.nn.MSFT$mean), col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```



## for NVDA

```{r}

trainID.NVDA = which(NVDA.data.Complete[,4]=="TRUE")
testID.NVDA = which(NVDA.data.Complete[,4]=="FALSE")

train.new.NVDA = NVDA.data.Complete[trainID.NVDA,]
test.new.NVDA = NVDA.data.Complete[testID.NVDA,]


fit.nn.NVDA <- nnetar(as.numeric(train.new.NVDA[,2]), xreg =  cbind(as.numeric(train.new.NVDA[,1]), as.numeric(train.new.NVDA[,3])), lambda="auto", decay = 0.1)

fit_test_cv.NVDA <- CVar(as.numeric(train.new.NVDA[,2]), xreg =  cbind(as.numeric(train.new.NVDA[,1]), as.numeric(train.new.NVDA[,3])), lambda="auto", decay = 0.1)

fit.nn.NVDA

fore.nn.NVDA <- forecast::forecast(fit.nn.NVDA, xreg =  cbind(as.numeric(test.new.NVDA[,1]), as.numeric(test.new.NVDA[,3])), PI = TRUE)

## mean square error
MSE.nnetar.NVDA <- mean((fore.nn.NVDA$mean - as.numeric(test.new.NVDA[,2]))^2)
MSE.nnetar.NVDA

## mean absolute deviation
MAD.nnetar.NVDA <- mean(abs(fore.nn.NVDA$mean - as.numeric(test.new.NVDA[,2])))
MAD.nnetar.NVDA
```



```{r}
plot(as.numeric(test.new.NVDA[,2]), col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(as.vector(fore.nn.NVDA$mean), col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```




## for INTC

```{r}

trainID.INTC = which(INTC.data.Complete[,4]=="TRUE")
testID.INTC = which(INTC.data.Complete[,4]=="FALSE")

train.new.INTC = INTC.data.Complete[trainID.INTC,]
test.new.INTC = INTC.data.Complete[testID.INTC,]


fit.nn.INTC <- nnetar(as.numeric(train.new.INTC[,2]), xreg =  cbind(as.numeric(train.new.INTC[,1]), as.numeric(train.new.INTC[,3])), lambda="auto", decay = 0.1)

fit_test_cv.INTC <- CVar(as.numeric(train.new.INTC[,2]), xreg =  cbind(as.numeric(train.new.INTC[,1]), as.numeric(train.new.INTC[,3])), lambda="auto", decay = 0.1)

fit.nn.INTC

fore.nn.INTC <- forecast::forecast(fit.nn.INTC, xreg =  cbind(as.numeric(test.new.INTC[,1]), as.numeric(test.new.INTC[,3])), PI = TRUE)

## mean square error
MSE.nnetar.INTC <- mean((fore.nn.INTC$mean - as.numeric(test.new.INTC[,2]))^2)
MSE.nnetar.INTC

## mean absolute deviation
MAD.nnetar.INTC <- mean(abs(fore.nn.INTC$mean - as.numeric(test.new.INTC[,2])))
MAD.nnetar.INTC
```



```{r}
plot(as.numeric(test.new.INTC[,2]), col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(as.vector(fore.nn.INTC$mean), col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```





## NN with two layers. each layer has 24 neurons


## AAPL

```{r}
model.AAPL.new <- keras_model_sequential() %>%
  layer_simple_rnn(units = 24, input_shape = list(11, 3),
                   dropout = 0.1, recurrent_dropout = 0.1,
                   return_sequences = TRUE) %>%
  layer_simple_rnn(units = 24,
                   dropout = 0.1, recurrent_dropout = 0.1) %>%
  layer_dense(units = 1)

model.AAPL.new %>% compile(optimizer = optimizer_rmsprop(), loss = "mse")


history.AAPL.new <- model.AAPL.new %>% fit(xrnn.AAPL[(1:ntest) ,, ], arframe.AAPL[(1:ntest) , "log_volume.AAPL"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) ,, ], arframe.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) , "log_volume.AAPL"]))

kpred.AAPL.new <- predict(model.AAPL.new, xrnn.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) ,, ])

## mean square error
MSE.AAPL.new <- mean((kpred.AAPL.new - arframe.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) , "log_volume.AAPL"])^2)
MSE.AAPL.new

## mean absolute deviation
MAD.AAPL.new <- mean(abs(kpred.AAPL.new - arframe.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) , "log_volume.AAPL"]))
MAD.AAPL.new

```



```{r}
plot(arframe.AAPL[((ntest+1):(dim(xrnn.AAPL)[1])) , "log_volume.AAPL"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.AAPL.new, col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```




## MSFT

```{r}
model.MSFT.new <- keras_model_sequential() %>%
  layer_simple_rnn(units = 24, input_shape = list(14, 3),
                   dropout = 0.1, recurrent_dropout = 0.1,
                   return_sequences = TRUE) %>%
  layer_simple_rnn(units = 24,
                   dropout = 0.1, recurrent_dropout = 0.1) %>%
  layer_dense(units = 1)

model.MSFT.new %>% compile(optimizer = optimizer_rmsprop(), loss = "mse")


history.MSFT.new <- model.MSFT.new %>% fit(xrnn.MSFT[(1:ntest) ,, ], arframe.MSFT[(1:ntest) , "log_volume.MSFT"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) ,, ], arframe.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) , "log_volume.MSFT"]))

kpred.MSFT.new <- predict(model.MSFT.new, xrnn.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) ,, ])

## mean square error
MSE.MSFT.new <- mean((kpred.MSFT.new - arframe.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) , "log_volume.MSFT"])^2)
MSE.MSFT.new

## mean absolute deviation
MAD.MSFT.new <- mean(abs(kpred.MSFT.new - arframe.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) , "log_volume.MSFT"]))
MAD.MSFT.new

```



```{r}
plot(arframe.MSFT[((ntest+1):(dim(xrnn.MSFT)[1])) , "log_volume.MSFT"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.MSFT.new, col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```






## NVDA

```{r}
model.NVDA.new <- keras_model_sequential() %>%
  layer_simple_rnn(units = 24, input_shape = list(4, 3),
                   dropout = 0.1, recurrent_dropout = 0.1,
                   return_sequences = TRUE) %>%
  layer_simple_rnn(units = 24,
                   dropout = 0.1, recurrent_dropout = 0.1) %>%
  layer_dense(units = 1)

model.NVDA.new %>% compile(optimizer = optimizer_rmsprop(), loss = "mse")


history.NVDA.new <- model.NVDA.new %>% fit(xrnn.NVDA[(1:ntest) ,, ], arframe.NVDA[(1:ntest) , "log_volume.NVDA"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) ,, ], arframe.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) , "log_volume.NVDA"]))

kpred.NVDA.new <- predict(model.NVDA.new, xrnn.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) ,, ])

## mean square error
MSE.NVDA.new <- mean((kpred.NVDA.new - arframe.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) , "log_volume.NVDA"])^2)
MSE.NVDA.new

## mean absolute deviation
MAD.NVDA.new <- mean(abs(kpred.NVDA.new - arframe.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) , "log_volume.NVDA"]))
MAD.NVDA.new

```



```{r}
plot(arframe.NVDA[((ntest+1):(dim(xrnn.NVDA)[1])) , "log_volume.NVDA"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.NVDA.new, col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```







## INTC

```{r}
model.INTC.new <- keras_model_sequential() %>%
  layer_simple_rnn(units = 24, input_shape = list(4, 3),
                   dropout = 0.1, recurrent_dropout = 0.1,
                   return_sequences = TRUE) %>%
  layer_simple_rnn(units = 24,
                   dropout = 0.1, recurrent_dropout = 0.1) %>%
  layer_dense(units = 1)

model.INTC.new %>% compile(optimizer = optimizer_rmsprop(), loss = "mse")


history.INTC.new <- model.INTC.new %>% fit(xrnn.INTC[(1:ntest) ,, ], arframe.INTC[(1:ntest) , "log_volume.INTC"],
batch_size = 64, epochs = 200, validation_data =
list(xrnn.INTC[((ntest+1):(dim(xrnn.INTC)[1])) ,, ], arframe.INTC[((ntest+1):(dim(xrnn.INTC)[1])) , "log_volume.INTC"]))

kpred.INTC.new <- predict(model.INTC.new, xrnn.INTC[((ntest+1):(dim(xrnn.INTC)[1])) ,, ])

## mean square error
MSE.INTC.new <- mean((kpred.INTC.new - arframe.INTC[((ntest+1):(dim(xrnn.INTC)[1])) , "log_volume.INTC"])^2)
MSE.INTC.new

## mean absolute deviation
MAD.INTC.new <- mean(abs(kpred.INTC.new - arframe.INTC[((ntest+1):(dim(xrnn.INTC)[1])) , "log_volume.INTC"]))
MAD.INTC.new

```



```{r}
plot(arframe.INTC[((ntest+1):(dim(xrnn.INTC)[1])) , "log_volume.INTC"], col="red", type="l", ylab = "Log Trading Volume", xlab = "Day")
lines(kpred.INTC.new, col="blue")
legend("bottomright", legend = c("Actuals", "Forecasts"), col = c("red", "blue"), lty = 1, lwd = 2)
```





